Online Updating of Variational Bayes for Forecasts of Vehicle Trajectory with Heterogeneous Driver Behaviour

### 2018-02-08 Cars/paper.tex
misc

\subsubsection{Neural Networks}

Following Ding et al. (2012), a Neural Network is constructed with inputs given by the ten most recent lags of vehicle position, angle, and velocity, and an output given by the next thirty values of the vehicle position. The network is trained with the Adam optimised with a mean Euclidean error loss function. 
\subsection{Results}

>>>>

\subsubsection{Recurrent Neural Networks}

A Recurrent Neural Network is constructed with inputs given by the ten most recent lags of vehicle position, angle, and velocity, and an output given by the next thirty values of the vehicle position. The network is trained with the Adam optimiser and a mean Euclidean error loss function. 
\subsection{Results}
